models with mice

### 2024-03-27 Paper1.Rmd
cfa for coal fixed

#kable_table <- kable(correlation_df, caption = "Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", #digits = 2) %>%
  #kable_styling(full_width = F) %>%
  #column_spec(1, background = "white") %>%
  #add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))#%>%
  #pack_rows("Perceived Risks", 1, nrow(correlation_df))

# Apply alternating background colors for columns
#for (i in seq(2, ncol(correlation_df), by = 2)) {
  #kable_table <- kable_table %>%

#row_spec(i, background = "#F0F0F0")
#}

# Print the kable table
#print(kable_table)
```

>>>>

kable_table <- kable(correlation_df, caption = " Table 8 : Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", digits = 2) %>%
  kable_styling(full_width = F) %>%
  column_spec(1, background = "white") %>%
  add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))%>%
  pack_rows("Perceived Risks", 1, nrow(correlation_df))

# Apply alternating background colors for columns
for (i in seq(2, ncol(correlation_df), by = 2)) {
  kable_table <- kable_table %>% 
row_spec(i, background = "#F0F0F0")
}

# Print the kable table
print(kable_table)
```

### 2024-03-27 withmice.Rmd
cfa for coal fixed

# EFA with mifa

ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 2, rotate = "varimax")

#print.psych(ecopolfits, sort= TRUE, cut= 0.4)

@@

ecopols_2fa <- '
  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR
  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR +ENVOVERDEV
'

@@

# Confirmatory Factor Analysis(CFA): Solar

@@

# EFA With mifa - all ecopol vars for coal
ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")

@@

# (DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,RELYCOAL)

@@

ecopolc_2fa <- '
  Ndevelop =~ DEVCOAL+ PROSPERCOAL + NPRIDECOAL + PRIDECOAL  + JOBSCOAL + ECONOMYGLOBAL+ WEALTHLIM+ INDUSTRYLARGE+ DECISIONCEN + MECHANISATION + DEVOVERENV
  Pdevelop =~ BEAUTYCOAL + + HEALTHCOAL + POLLUTECOAL 
  Pdevelop2 =~  DISPLACECOAL  + ENVOVERDEV +OWNERPUB

@@

cparams1$Scale <- NA
cparams1$Scale[1:8] <- "People Centered Development"
cparams1$Scale[9:14] <- "Nationalist Development"
cparams1 <- cparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
CFAcoal <- knitr::kable(cparams1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on eco-pol scale (Coal)") %>%
  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
  column_spec(column = 2, width = "4cm")

>>>>

# EFA with mifamiecopols$cov_combined

ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 3, rotate = "varimax")

print.psych(ecopolfits, sort= TRUE, cut= 0.4)

@@

ecopols_2fa <- '
  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR
  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR 
'

@@

### Confirmatory Factor Analysis(CFA): Solar

@@

# EFA With mifa - all ecopol vars for coal
ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 2, rotate = "varimax")

@@

# (DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,RELYCOAL)
#+ DECISIONCEN + MECHANISATION + DEVOVERENV+ JOBSCOAL 
# + ENVOVERDEV + OWNERPUB

@@

ecopolc_2fa <- '
  Ndevelop =~ NPRIDECOAL + PRIDECOAL + DEVOVERENV + DEVCOAL
  Pdevelop1 =~ BEAUTYCOAL + HEALTHCOAL + POLLUTECOAL 
  Pdevelop2 =~ DISPLACECOAL + ENVOVERDEV + OWNERPUB

@@

cparams1$Scale <- NA
cparams1$Scale[1:5] <- "Nationalist Development"
cparams1$Scale[6:14] <- "People Centered Development (1)"
cparams1$Scale[9:14] <- "People Centered Development (2)"
cparams1 <- cparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
CFAcoal <- knitr::kable(cparams1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on eco-pol scale (Coal)") %>%
  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
  column_spec(column = 2, width = "4cm")
